### 2017-07-09 README.Rmd
added AppVeyor support

[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![Build Status](https://travis-ci.org/bgreenwell/pdp.svg?branch=master)](https://travis-ci.org/bgreenwell/pdp)
[![Coverage Status](https://img.shields.io/codecov/c/github/bgreenwell/pdp.svg)](https://codecov.io/github/bgreenwell/pdp?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/pdp)](http://cranlogs.r-pkg.org/badges/pdp)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)
[![Rdoc](http://www.rdocumentation.org/badges/version/pdp)](http://www.rdocumentation.org/packages/pdp)

>>>>

[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![Build Status](https://travis-ci.org/bgreenwell/pdp.svg?branch=master)](https://travis-ci.org/bgreenwell/pdp)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/bgreenwell/pdp?branch=master&svg=true)](https://ci.appveyor.com/project/bgreenwell/pdp)
[![Coverage Status](https://img.shields.io/codecov/c/github/bgreenwell/pdp.svg)](https://codecov.io/github/bgreenwell/pdp?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/pdp)](http://cranlogs.r-pkg.org/badges/pdp)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)
